\LARGE \bf \pyRobots, a toolkit for robot executive control

### 2014-08-20 paper.tex
WIP on the Concepts and Overview

\section{Concepts}

Before introducing and explaining step-by-step a complete example in the next
section, it is useful to introduce the main concepts of \pyRobots.

\begin{itemize}
    \item Turns any Python function into a background action with the decorator
        \python|@action|.
    \item Robot actions are non-blocking by default: they are instanciated as
        futures (lightweight threads),
    \item Actions can be cancelled at any time via signals (the
        \python|ActionCancelled| signal is raised).
    \item Lock specific resources with a simple \python|@lock(...)| in front of the
        actions. When starting, actions will wait for resources to be
        available if needed.
    \item Supports compound resources (like \python|WHEELS == LEFTWHEEL + RIGHTWHEEL|)
    \item Create event with robot.every(<condition>).do(<action>)
    \item Poses are managed explicitely and can easily be
        transformed from one reference frame to another one
        (integrates with ROS TF when available).
    \item Extensive logging support to debug and replay
        experiments.
\end{itemize}

\section{Example}

>>>>

\section{Concepts and Overview}

Before introducing and explaining step-by-step a complete working example in the next
section, it is useful to first introduce the main concepts of \pyRobots, and
provide an overview of the features and mechanisms.

\begin{itemize}
    \item Turns any Python function into a background action with the decorator
        \python|@action|.
    \item Robot actions are non-blocking by default: they are instanciated as
        futures (lightweight threads),
    \item Actions can be cancelled at any time via signals (the
        \python|ActionCancelled| signal is raised).
    \item Lock specific resources with a simple \python|@lock(...)| in front of the
        actions. When starting, actions will wait for resources to be
        available if needed.
    \item Supports compound resources (like \python|WHEELS == LEFTWHEEL + RIGHTWHEEL|)
    \item Create event with robot.every(<condition>).do(<action>)
    \item Poses are managed explicitly and can easily be
        transformed from one reference frame to another one
        (integrates with ROS TF when available).
    \item Extensive logging support to debug and replay
        experiments.
\end{itemize}

\subsection{Core concepts}

\pyRobots core concepts are simple: on one hand, the user creates a
\textbf{robot} as an instance of a \python|GenericRobot|, that encapsulates the
different low-level \textbf{controllers} (proxies to actuators, typically
provided by a middleware like ROS) and the \textbf{state} of the robot
(typically a set proxies to the sensors, or a connector to a database, etc.).

On the other hand, the user creates as many high-level \textbf{actions} as
desired, as regular Python functions. Actions are automatically added to the
\textbf{robot}, and can access its state and controllers to perform actual
physical actions.

The user can list \textbf{events} that the \textbf{robot} must monitor, and
attach callback to them.

Finally, the user can declare arbitrary \textbf{resources}, usually
corresponding to the robot components (for instance, the wheels, the camera,...)
and guarantee exclusive access to the required resource to specific actions.

\subsection{Asynchronous actions}

As they will be executed in independent
threads, these functions may block or never return (typically useful to
implement lasting background behaviours).

Actions can also call each-other, allowing decomposition of
complex tasks into sub-actions and eventually atomic actions.

\subsection{Events}

\subsection{Resources management}

\subsection{Uniform management of rigid transformations and frames}

\subsection{Developer support: logging, debugging, introspection}
\label{}

\section{Implementation and Example}
